### 2015-05-11 Draft/approach.tex
ASE Changes

The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API classify the unlabeled sentences as being temporal constraints or not.
From an implementation perspective, we can use any of the standard off-the-shelf classifiers to train the ML model, since \tool\ seeks to achieve only a binary classification of the API sentences.
For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
The ML model can be trained offline or else by the users of the approach if better accuracy is desired for domain-specific data.

>>>>

The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API classify the unlabeled sentences as being temporal constraints or not.
From an implementation perspective, we can use any of the standard off-the-shelf classifiers to train the ML model, since \tool\ seeks to achieve only a binary classification of the API sentences.
For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate preprocessing~\cite{rennie2003tackling}.
The ML model can be trained offline or else by the users of the approach if better accuracy is desired for domain-specific data.

### 2015-05-11 Draft/background.tex
ASE Changes

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state-of-the-art approaches have demonstrated to be effective in classifying POS tags for well-written news articles.

>>>>

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'} and \textit{`grammatical tagging'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state-of-the-art approaches have demonstrated to be effective in classifying POS tags for well-written news articles.

### 2015-05-11 Draft/evaluation.tex
Dr. Xie's cmnts on Abstract, Intro, and Conclusion
ASE Changes

$F-Score$ = $\frac{2 X Precison X Recall}{Precision + Recall}$
\end{center}

@@

\begin{tabular}{lccccc}
\topline
\headcol 	API 			& Mtds 	& Sen 	& Sen$_C$ 	& Spec$_{ICON}$ 	& Acc(\%)\\
\midline 
			java.io 		& 662 	& 2417 	& 78 		& 56 				& 71.8\\ 
\rowcol 	Amazon S3 REST 	& 51 	& 1492 	& 12		& 7 				& 58.3\\ 
			Paypal REST 	& 33	& 151 	& 20 		& 14				& 70.0\\ 
\rowcol 	Total 			& 746 	& 4060 	& 110		& 77 				& 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{6}{p{3.25in}}{\small
$^*$ Average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table}

@@

In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
Column ``Trainer'' lists the names of the subject API. 
Columns ``Mtds'' and ``Sen'' list the number of methods and sentences in each subject API's.
Column ``Sen$_C$'' lists the number of manually identified constraint sentences.
Column ``Spec$_{ICON}$'' lists the number of sentences with correctly inferred temporal constraints by \tool. 
Column ``Acc(\%)'' list percentage values of accuracy. 
Our results show that, out of 90 manually identified constraint sentences, \tool\ correctly infers temporal constraints with the average accuracy of 70.0\%.

@@

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluation are representative of true practice. To minimize the threat, we used API documents of three different API's: JDK \CodeIn{java.io}, \amazonAPI, \paypalAPI. On one hand, Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages. In contrast, \amazonAPI\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language. Finally, \paypalAPI\ provides a REST support for online financial transactions. The difference in the functionalities provided by the three API's also address the issue of over-fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects API's.

>>>>

$F-Score$ = $\frac{2 X Precision X Recall}{Precision + Recall}$
\end{center}

@@

\begin{tabular}{lccccc}
\topline
\headcol 	API 			& Mtds 	& Sen 	& Sen$_C$ 	& Spec$_{ICON}$ 	& Acc(\%)\\
\midline 
			java.io 		& 662 	& 2417 	& 78 		& 56 				& 71.8\\ 
\rowcol 	Amazon S3 REST 	& 51 	& 1492 	& 12		& 7 				& 58.3\\ 
			Paypal REST 	& 33	& 151 	& 20 		& 14				& 70.0\\ 
\rowcol 	Total 			& 746 	& 4060 	& 110		& 77 				& 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{6}{p{3.25in}}{\small
$^*$ Average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraints correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table}

@@

In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
Column ``API'' lists the names of the subject API. 
Columns ``Mtds'' and ``Sen'' list the number of methods and sentences in each subject API's.
Column ``Sen$_C$'' lists the number of manually identified constraint sentences.
Column ``Spec$_{ICON}$'' lists the number of sentences with correctly inferred temporal constraints by \tool. 
Column ``Acc(\%)'' list percentage values of accuracy. 
Our results show that, out of 90 manually identified constraint sentences, \tool\ correctly infers temporal constraints with the average accuracy of 70.0\%.

@@

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluation are representative of true practice. To minimize the threat, we used API documents of three different API's: JDK \CodeIn{java.io}, \amazonAPI, \paypalAPI. On one hand, Java is a widely used programming language and \CodeIn{java.io} is one of the main packages. In contrast, \amazonAPI\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language. Finally, \paypalAPI\ provides a REST support for online financial transactions. The difference in the functionalities provided by the three API's also address the issue of over-fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects API's.
